Supplement A to 'Researchers understand and use the logic of significance testing in a novel statistical reasoning task

### 2020-02-07 inst/manuscript/manuscript.Rmd
made Lato the default font for ggplot graphs

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      out.width = "0.95\\textwidth")

@@

```{r error_rates, fig.cap="Decision error rates as a function of true effect size. The red solid line represents the rate at which participants {\\em correctly} determined the direction of the effect, except for at an effect size of 0, where it represents an incorrect claim of an effect. The shaded region around the solid line is one standard error wide. The difference between the black and the gray dashed lines shows the proportion of participants who decided that the two groups were the same (as opposed to failing to detect a difference)."}
MoreyHoekstra2019::fig_error_rates()
```

>>>>

MoreyHoekstra2019::pkg_options(ggplot_family="Lato Light")

knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE,
                      message = FALSE,
                      out.width = "0.95\\textwidth",
                      dev = "cairo_pdf")

@@

```{r error_rates, fig.cap="Decision error rates as a function of true effect size. The red solid line represents the rate at which participants {\\em correctly} determined the direction of the effect, except for at an effect size of 0, where it represents an incorrect claim of an effect. The shaded region around the solid line is one standard error wide. The difference between the black and the gray dashed lines shows the proportion of participants who decided that the two groups were the same (as opposed to failing to detect a difference).", fig.showtext=FALSE}
MoreyHoekstra2019::fig_error_rates()
```

### 2020-02-07 inst/manuscript/supplementA.Rmd
made Lato the default font for ggplot graphs

```{r pvals-q3, echo = FALSE, out.width='100%', fig.cap="Selected two-sided $p$ values for the null distribution of the evidence for the wide evidence distribution ($q=3$)"}
fn = MoreyHoekstra2019::fig_evidence_p_vals(q = 3, letter = "q=3")
knitr::include_graphics(fn)

@@

```{r shuffle-understanding, fig.caption="Frequencies of responses to the initial question, \"Do you understand why the random shuffle reports could be useful?\""}
MoreyHoekstra2019::fig_shuffle_understanding()
```

@@

```{r sampling, fig.cap="Sampling behavior by effect size. Each point represents a participant. A: Number of samples from the null distribution as a function of true effect size. B: Number of samples of fictional 'experiments' as a function of true effect size. Note that the $y$ axis is logarithmically scaled. Lines are robust regression fits (Venables \\& Ripley, 2002)."}
MoreyHoekstra2019::fig_sampling_behavior()
```

@@

```{r strategies, fig.cap="Coded frequencies of different strategies in the open-ended responses. A \"Strong\" indicates use of comparison to the null distribution or  its use to assess sampling variability/distribution. A \"Weak only\" response indicates some indication of symmetry or asymmetry (or its use as a strategy)."}
MoreyHoekstra2019::fig_strategies()
```

@@

```{r fig.cap="Proportion who have a \"difference\" response as a function of effect size, for participants who were coded as reported 0, 1, or 2 strong significance testing strategies. Ribbons are standard errors."}

@@

dat %>%
    mutate(effect_size = abs(effect_size),
           `# strong` = factor(n_strong)) %>%
    group_by(effect_size, true_winner, response, `# strong`) %>%
    tally() %>%
    complete(effect_size, true_winner, response, `# strong`, fill = list(n = 0)) %>%
    ungroup() %>%
    filter(response != "bored") %>%
    mutate(
      dec_type = case_when(
        true_winner != "null" &
          true_winner != response &
          response %in% c("jinglies", "sparklies") ~ "sign_error",
        response %in% c("jinglies", "sparklies") ~ "report_difference",
        response == "same" ~ "same",
        response == "no_detect" ~ "no_detect"
      )
    ) %>%
    group_by(dec_type, effect_size, `# strong`) %>%
    tally( wt = n ) %>%
    complete(dec_type, effect_size, `# strong`, fill = list(n = 0)) %>%
    group_by(effect_size, `# strong`) %>%
    mutate(total = sum(n)) %>%
  filter(dec_type == "report_difference") %>%
  mutate(
      p = n / total,
      stderr = sqrt(p * (1 - p) / total),
      lo = qlogis(p),
      lo.stderr = stderr / dlogis(qlogis(p))
    ) %>%
  select(-dec_type) %>% 
  ggplot(aes(x = effect_size, y = p, group = `# strong`)) +
      geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = 1,
      color = NA,
      fill = "#EEEEEE",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .8,
      ymax = 1,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .2,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .95,
      ymax = 1,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .05,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_segment(aes(
      x = 0,
      y = 0,
      xend = 0,
      yend = 1
    )) +
    geom_hline(yintercept = c(0, 1)) +
    geom_line(aes(linetype = `# strong`, col = `# strong`), size = .7) +
    geom_point(aes(col = `# strong`)) +
    geom_ribbon(aes(
      ymin = p - stderr,
      ymax = p + stderr,
      fill = `# strong`
    ),
    alpha = 0.2) +
      xlab("Effect size") + ylab("Proportion of responses") +
    coord_cartesian(
      ylim = c(0, 1.2),
      xlim = c(0, 1),
      expand = FALSE,
      clip = "off"
    ) +
    scale_y_continuous(breaks = seq(0, 1, .1)) +
    scale_x_continuous(breaks = seq(0, 1, .2)) +
    theme(
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.background = element_blank(),
      text = element_text()
    )

@@

```{r fig.cap="Boxes, in order from left to right (red, green, blue) are 0, 1, and 2 strong significance testing strategies, respectively. Lines are robust regression fits. Stars show participants who indicated they did not use the random shuffle reports. Null samples (left) order from bottom to top (0, 1, 2); experimental samples (right) order is (3, 0, 1) from bottom to top."}
cnull <- dat %>%
  split(.$n_strong) %>%
  map( ~ MASS::rlm(ln_null ~ effect_size, data = .)) %>%
  map_df(coef)

@@

# grouped boxplot
p1 = ggplot(dat,
            aes(
              x = effect_size,
              y = n_null,
              group = interaction(n_strong, effect_size),
              fill = factor(n_strong)
              )) +
  geom_boxplot() +
  scale_y_continuous(trans = 'log10') +
  theme(legend.position = "none") +
  ylab("Number of samples") + ggtitle("Null") +
  xlab("Effect size") +
  geom_abline(
    intercept = cnull$`0`[1],
    slope = cnull$`0`[2],
    color = scales::hue_pal()(2)[1]
    ) +
  geom_abline(
    intercept = cnull$`1`[1],
    slope = cnull$`1`[2],
    color = scales::hue_pal()(2)[2]
    ) +
  geom_abline(
    intercept = cnull$`2`[1],
    slope = cnull$`2`[2],
    color = scales::hue_pal()(3)[3]
    ) +
  geom_point(data = only_no_shuffle,
             mapping = aes(x = effect_size, 
                           y = n_null), 
             shape = 8,
             size = 3)

        # grouped boxplot
p2 = ggplot(dat,
            aes(
              x = effect_size,
              y = n_expt,
              group = interaction(n_strong, effect_size),
              fill = factor(n_strong)
              )) +
  geom_boxplot() +
  scale_y_continuous(trans = 'log10') +
  theme(legend.position = "none") +
  ylab("Number of samples") + ggtitle("Experiments") +
  xlab("Effect size") +
  geom_abline(
    intercept = cexpt$`0`[1],
    slope = cexpt$`0`[2],
    color = scales::hue_pal()(2)[1]
    ) +
  geom_abline(
    intercept = cexpt$`1`[1],
    slope = cexpt$`1`[2],
    color = scales::hue_pal()(2)[2]
    ) +
  geom_abline(
    intercept = cexpt$`2`[1],
    slope = cexpt$`2`[2],
    color = scales::hue_pal()(3)[3]
    ) +
    geom_point(data = only_no_shuffle,
             mapping = aes(x = effect_size, 
                           y = n_expt), 
             shape = 8,
             size = 3)

>>>>

```{r pvals-q3, echo = FALSE, out.width='100%', fig.cap="Selected two-sided $p$ values for the null distribution of the evidence for the wide evidence distribution ($q=3$)"}
fn = MoreyHoekstra2019::fig_evidence_p_vals(q = 3, letter = "q=3")
knitr::include_graphics(fn)
```

@@

```{r shuffle-understanding, fig.caption="Frequencies of responses to the initial question, \"Do you understand why the random shuffle reports could be useful?\"", fig.showtext=FALSE}
MoreyHoekstra2019::fig_shuffle_understanding()
```

@@

```{r sampling, fig.cap="Sampling behavior by effect size. Each point represents a participant. A: Number of samples from the null distribution as a function of true effect size. B: Number of samples of fictional 'experiments' as a function of true effect size. Note that the $y$ axis is logarithmically scaled. Lines are robust regression fits (Venables \\& Ripley, 2002).", fig.showtext=FALSE}
MoreyHoekstra2019::fig_sampling_behavior()
```

@@

```{r strategies, fig.cap="Coded frequencies of different strategies in the open-ended responses. A \"Strong\" indicates use of comparison to the null distribution or  its use to assess sampling variability/distribution. A \"Weak only\" response indicates some indication of symmetry or asymmetry (or its use as a strategy).", fig.showtext=FALSE}
MoreyHoekstra2019::fig_strategies()
```

@@

```{r fig.cap="Proportion who have a \"difference\" response as a function of effect size, for participants who were coded as reported 0, 1, or 2 strong significance testing strategies. Ribbons are standard errors.", fig.showtext=FALSE}

@@

dat %>%
    mutate(effect_size = abs(effect_size),
           `# strong` = factor(n_strong)) %>%
    group_by(effect_size, true_winner, response, `# strong`) %>%
    tally() %>%
    complete(effect_size, true_winner, response, `# strong`, fill = list(n = 0)) %>%
    ungroup() %>%
    filter(response != "bored") %>%
    mutate(
      dec_type = case_when(
        true_winner != "null" &
          true_winner != response &
          response %in% c("jinglies", "sparklies") ~ "sign_error",
        response %in% c("jinglies", "sparklies") ~ "report_difference",
        response == "same" ~ "same",
        response == "no_detect" ~ "no_detect"
      )
    ) %>%
    group_by(dec_type, effect_size, `# strong`) %>%
    tally( wt = n ) %>%
    complete(dec_type, effect_size, `# strong`, fill = list(n = 0)) %>%
    group_by(effect_size, `# strong`) %>%
    mutate(total = sum(n)) %>%
  filter(dec_type == "report_difference") %>%
  mutate(
      p = n / total,
      stderr = sqrt(p * (1 - p) / total),
      lo = qlogis(p),
      lo.stderr = stderr / dlogis(qlogis(p))
    ) %>%
  select(-dec_type) %>% 
  ggplot(aes(x = effect_size, y = p, group = `# strong`)) +
      geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = 1,
      color = NA,
      fill = "#EEEEEE",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .8,
      ymax = 1,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .2,
      color = NA,
      fill = "#DDDDDD",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = .95,
      ymax = 1,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_rect(
      xmin = 0,
      xmax = 1,
      ymin = 0,
      ymax = .05,
      color = NA,
      fill = "#CCCCCC",
      alpha = .1
    ) +
    geom_segment(aes(
      x = 0,
      y = 0,
      xend = 0,
      yend = 1
    )) +
    geom_hline(yintercept = c(0, 1)) +
    geom_line(aes(linetype = `# strong`, col = `# strong`), size = .7) +
    geom_point(aes(col = `# strong`)) +
    geom_ribbon(aes(
      ymin = p - stderr,
      ymax = p + stderr,
      fill = `# strong`
    ),
    alpha = 0.2) +
      xlab("Effect size") + ylab("Proportion of responses") +
    coord_cartesian(
      ylim = c(0, 1.2),
      xlim = c(0, 1),
      expand = FALSE,
      clip = "off"
    ) +
    scale_y_continuous(breaks = seq(0, 1, .1)) +
    scale_x_continuous(breaks = seq(0, 1, .2)) +
    theme(
      panel.grid.major.x = element_blank(),
      panel.grid.minor.x = element_blank(),
      panel.background = element_blank(),
      text = element_text(
        family = MoreyHoekstra2019::pkg_options("ggplot_family")
        )
    )

@@

```{r fig.cap="Boxes, in order from left to right (red, green, blue) are 0, 1, and 2 strong significance testing strategies, respectively. Lines are robust regression fits. Stars show participants who indicated they did not use the random shuffle reports. Null samples (left) order from bottom to top (0, 1, 2); experimental samples (right) order is (3, 0, 1) from bottom to top.", fig.showtext=FALSE}
cnull <- dat %>%
  split(.$n_strong) %>%
  map( ~ MASS::rlm(ln_null ~ effect_size, data = .)) %>%
  map_df(coef)

@@

# grouped boxplot
p1 = ggplot(dat,
            aes(
              x = effect_size,
              y = n_null,
              group = interaction(n_strong, effect_size),
              fill = factor(n_strong)
              )) +
  geom_boxplot() +
  scale_y_continuous(trans = 'log10') +
  theme(legend.position = "none",
        text = element_text(
          family = MoreyHoekstra2019::pkg_options("ggplot_family"))
        ) +
  ylab("Number of samples") + ggtitle("Null") +
  xlab("Effect size") +
  geom_abline(
    intercept = cnull$`0`[1],
    slope = cnull$`0`[2],
    color = scales::hue_pal()(2)[1]
    ) +
  geom_abline(
    intercept = cnull$`1`[1],
    slope = cnull$`1`[2],
    color = scales::hue_pal()(2)[2]
    ) +
  geom_abline(
    intercept = cnull$`2`[1],
    slope = cnull$`2`[2],
    color = scales::hue_pal()(3)[3]
    ) +
  geom_point(data = only_no_shuffle,
             mapping = aes(x = effect_size, 
                           y = n_null), 
             shape = 8,
             size = 3)

        # grouped boxplot
p2 = ggplot(dat,
            aes(
              x = effect_size,
              y = n_expt,
              group = interaction(n_strong, effect_size),
              fill = factor(n_strong)
              )) +
  geom_boxplot() +
  scale_y_continuous(trans = 'log10') +
  theme(legend.position = "none",
        text = element_text(
          family = MoreyHoekstra2019::pkg_options("ggplot_family"))
        ) +
  ylab("Number of samples") + ggtitle("Experiments") +
  xlab("Effect size") +
  geom_abline(
    intercept = cexpt$`0`[1],
    slope = cexpt$`0`[2],
    color = scales::hue_pal()(2)[1]
    ) +
  geom_abline(
    intercept = cexpt$`1`[1],
    slope = cexpt$`1`[2],
    color = scales::hue_pal()(2)[2]
    ) +
  geom_abline(
    intercept = cexpt$`2`[1],
    slope = cexpt$`2`[2],
    color = scales::hue_pal()(3)[3]
    ) +
    geom_point(data = only_no_shuffle,
             mapping = aes(x = effect_size, 
                           y = n_expt), 
             shape = 8,
             size = 3)
